Methods for Large Scale Learning to Rank

### 2014-03-12 report/Chapters/RelatedWork.tex
naar aanleiding van forward search, een nieuwe referentie voor BL-MART

Ganjisaffar \cite{Ganjisaffar2011b} proposed a pairwise boosting-wrapped-in-bagging model called BL-MART, in contrast to BagBoo which is a pointwise model. BL-MART adds a bagging step to the LambdaMART \cite{Wu2008} ranking model, a model that uses the Gradient Boosting \cite{Friedman2002} ensemble method combined with regression tree weak learners. In contract to BagBoo, BL-MART is limited in the number of trees. An experiment on the TD2004 dataset resulted in 4500 trees using BL-MART while 1.1 million trees were created with the BagBoo model.

@@

Lee and Lin \cite{Lee2014} describe a lower time complexity method to train a linear kernel RankSVM \cite{Herbrich1999, Joachims2002}. The authors observed that linear kernel RankSVMs are inferior in accuracy compared to nonlinear kernel RankSVMs and \ac{GBDT}s and are mainly useful to quickly produce a baseline model. Details of the lower time complexity version of the linear kernel RankSVM will not be discussed as it is shown to be an inferior Learning-to-Rank method in terms of accuracy.

>>>>

Ganjisaffar et al. \cite{Ganjisaffar2011c, Ganjisaffar2011b} proposed a pairwise boosting-wrapped-in-bagging model called BL-MART, in contrast to BagBoo which is a pointwise model. BL-MART adds a bagging step to the LambdaMART \cite{Wu2008} ranking model, a model that uses the Gradient Boosting \cite{Friedman2002} ensemble method combined with regression tree weak learners. In contract to BagBoo, BL-MART is limited in the number of trees. An experiment on the TD2004 dataset resulted in 4500 trees using BL-MART while 1.1 million trees were created with the BagBoo model.

@@

Lee and Lin \cite{Lee2014} describe a lower time complexity method to train a linear kernel RankSVM \cite{Herbrich1999, Joachims2002}. The authors observed that linear kernel RankSVMs are inferior in accuracy compared to nonlinear kernel RankSVMs and \ac{GBDT}s and are mainly useful to quickly produce a baseline model. Details of the lower time complexity version of the linear kernel RankSVM will not be discussed as it is shown to be an inferior Learning-to-Rank method in terms of accuracy.\\
